---
title: "220930_R_CreativeTerritoryTesting"
author: "Alison C. Holland"
date: "2022-09-30"
output: html_document
---

Download and load libraries
```{r}
# download libraries
#install.packages("DBI") # needed for dplyr
#install.packages("Rcpp") # needed for dplyr
#install.packages("plyr")
#install.packages("dplyr")
#install.packages("tidyr")
#install.packages("readxl")
#install.packages("ggplot2")
#install.packages("fmsb")
#install.packages("data.table")
#install.packages("janitor")
#install.packages("psych")
#install.packages("likert")
#install.packages("stopwords")
#install.packages("rJava")
#install.packages("qdap")
#install.packages("tm")
#install.packages("tidytext")
#install.packages("stringr")

# load libraries
library(DBI) # needed for dplyr
library(Rcpp) # needed for dplyr
library(plyr)
library(dplyr)
library(tidyr)
library(readxl)
library(ggplot2)
library(fmsb)
#library(data.table)
library(janitor)
library(psych)
library(likert)
library(stopwords)
library(qdap)
library(tm)
library(tidytext)
library(stringr)
```

Get and set working directory
```{r}
# get working directory
getwd()

# set working directory
setwd("/Users/xxx")
getwd()
```


Satisfaction Ratings
--------------------

Load and organise data
```{r}
# load data
data_concept1 <- read_excel("221118_CTT_UK_concept1_data.xlsx")
data_concept2 <- read_excel("221118_CTT_UK_concept2_data.xlsx")
data_concept3 <- read_excel("221118_CTT_UK_concept3_data.xlsx")
data_concept4 <- read_excel("221118_CTT_UK_concept4_data.xlsx")

#data_concept1 <- read_excel("221124_CTT_DE_concept1_dataEN.xlsx")
#data_concept2 <- read_excel("221124_CTT_DE_concept2_dataEN.xlsx")
#data_concept3 <- read_excel("221124_CTT_DE_concept3_dataEN.xlsx")
#data_concept4 <- read_excel("221124_CTT_DE_concept4_dataEN.xlsx")

# rename columns in all 4 
# concept 1
names(data_concept1) <- c(
  "countryGroup",
  "userGroup",
  "conceptGroup",
  "conceptNum",
  # impressions
  "describeConcept",
  # preference
  "missing",
  "confusing",
  "satisfactionRating_concept1",
  # emotional ties
  "happy",
  "satisfied",
  "appreciated", 
  "excited",
  "angry",
  "stressful",
  "disappointed",
  "relieved",
  "frustrated",
  "anxious",
  "confused",
  "confident",
  "other",
  # demographics
  "exams",
  "country",
  "age",
  "subjectStudying")

# remove weird extra columns (formating crap)
data_concept1 <- data_concept1 %>%
  select(1:25)

# add in ID column
data_concept1$ID <- seq.int(nrow(data_concept1))

# move ID column to first column
data_concept1 <- data_concept1 %>%
  select(ID, everything())

# concept 2
names(data_concept2) <- c(
  "countryGroup",
  "userGroup",
  "conceptGroup",
  "conceptNum",
  # impressions
  "describeConcept",
  # preference
  "missing",
  "confusing",
  "satisfactionRating_concept2",
  # emotional ties
  "happy",
  "satisfied",
  "appreciated", 
  "excited",
  "angry",
  "stressful",
  "disappointed",
  "relieved",
  "frustrated",
  "anxious",
  "confused",
  "confident",
  "other",
  # demographics
  "exams",
  "country",
  "age",
  "subjectStudying")

# add in ID column
data_concept2$ID <- seq.int(nrow(data_concept2))

# move ID column to first column
data_concept2 <- data_concept2 %>%
  select(ID, everything())

# concept 3
names(data_concept3) <- c(
  "countryGroup",
  "userGroup",
  "conceptGroup",
  "conceptNum",
  # impressions
  "describeConcept",
  # preference
  "missing",
  "confusing",
  "satisfactionRating_concept3",
  # emotional ties
  "happy",
  "satisfied",
  "appreciated", 
  "excited",
  "angry",
  "stressful",
  "disappointed",
  "relieved",
  "frustrated",
  "anxious",
  "confused",
  "confident",
  "other",
  # demographics
  "exams",
  "country",
  "age",
  "subjectStudying")

# add in ID column
data_concept3$ID <- seq.int(nrow(data_concept3))

# move ID column to first column
data_concept3 <- data_concept3 %>%
  select(ID, everything())

# concept 4
names(data_concept4) <- c(
  "countryGroup",
  "userGroup",
  "conceptGroup",
  "conceptNum",
  # impressions
  "describeConcept",
  # preference
  "missing",
  "confusing",
  "satisfactionRating_concept4",
  # emotional ties
  "happy",
  "satisfied",
  "appreciated", 
  "excited",
  "angry",
  "stressful",
  "disappointed",
  "relieved",
  "frustrated",
  "anxious",
  "confused",
  "confident",
  "other",
  # demographics
  "exams",
  "country",
  "age",
  "subjectStudying")

# remove weird extra columns (formating crap)
data_concept4 <- data_concept4 %>%
  select(1:25)

# add in ID column
data_concept4$ID <- seq.int(nrow(data_concept4))

# move ID column to first column
data_concept4 <- data_concept4 %>%
  select(ID, everything())


# count distinct ratings per concept and show ratings to plug into graphs 
data_concept1_rating <- table(data_concept1$satisfactionRating_concept1)
data_concept1_rating

data_concept2_rating <- table(data_concept2$satisfactionRating_concept2)
data_concept2_rating

data_concept3_rating <- table(data_concept3$satisfactionRating_concept3)
data_concept3_rating

data_concept4_rating <- table(data_concept4$satisfactionRating_concept4)
data_concept4_rating

```


Create Likert scale graph of all 4 concepts
-------------------------------------------

Source: https://jakec007.github.io/2021-06-23-R-likert/ 

Take numbers from above and turn into percentages - need totals also. Then add in percentages below. 

```{r}
Item <- c("Concept 1", "Concept 2", "Concept 3", "Concept 4")
star_1 <- c(2.06, 0.52, 1.62, 1.62)
star_2 <- c(7.22, 5.15, 3.24, 8.11)
star_3 <- c(15.98, 15.98, 15.68, 23.78)
star_4 <- c(39.18, 39.69, 37.30, 34.59)
star_5  <- c(35.57, 38.66, 42.16, 31.89)
df <- data.frame(Item, star_1, star_2, star_3, star_4, star_5)

# Rename Cols (for legend)
df <- df %>% 
  rename("1 star" = star_1,
         "2 stars" = star_2,
         "3 stars" = star_3,
         "4 stars" = star_4,
         "5 stars" = star_5)

# Pretty Plot (Image Below)
plot(likert(summary = df), 
     group.order = c("Concept 1", "Concept 2", "Concept 3", "Concept 4"), 
     legend.position = "right")

```

What kind of descriptive words or emotions are associated with each concept?
- positive
```{r}
# concept 1
# select columns
data_emos_pos_concept1 <- data_concept1 %>%
  dplyr::select(ID,
                happy,
                satisfied,
                appreciated,
                excited,
                relieved,
                confident) %>%
  # filter last row (already counted totals)
  filter(ID == 195) %>%
  # gather columns into rows
  gather("pos_emotions", "concept1_count", 2:7)

# change "count" column to numeric
data_emos_pos_concept1$concept1_count <- as.numeric(data_emos_pos_concept1$concept1_count)

# remove ID column
data_emos_pos_concept1 <- data_emos_pos_concept1[, -c(1)]


# concept 2
# select columns
data_emos_pos_concept2 <- data_concept2 %>%
  dplyr::select(ID,
                happy,
                satisfied,
                appreciated,
                excited,
                relieved,
                confident) %>%
  # filter last row (already counted totals)
  filter(ID == 195) %>%
  # gather columns into rows
  gather("pos_emotions", "concept2_count", 2:7)

# change "count" column to numeric
data_emos_pos_concept2$concept2_count <- as.numeric(data_emos_pos_concept2$concept2_count)

# remove ID column
data_emos_pos_concept2 <- data_emos_pos_concept2[, -c(1)]


# concept 3
# select columns
data_emos_pos_concept3 <- data_concept3 %>%
  dplyr::select(ID,
                happy,
                satisfied,
                appreciated,
                excited,
                relieved,
                confident) %>%
  # filter last row (already counted totals)
  filter(ID == 186) %>%
  # gather columns into rows
  gather("pos_emotions", "concept3_count", 2:7)

# change "count" column to numeric
data_emos_pos_concept3$concept3_count <- as.numeric(data_emos_pos_concept3$concept3_count)

# remove ID column
data_emos_pos_concept3 <- data_emos_pos_concept3[, -c(1)]


# concept 4
# select columns
data_emos_pos_concept4 <- data_concept4 %>%
  dplyr::select(ID,
                happy,
                satisfied,
                appreciated,
                excited,
                relieved,
                confident) %>%
  # filter last row (already counted totals)
  filter(ID == 186) %>%
  # gather columns into rows
  gather("pos_emotions", "concept4_count", 2:7)

# change "count" column to numeric
data_emos_pos_concept4$concept4_count <- as.numeric(data_emos_pos_concept4$concept4_count)

# remove ID column
data_emos_pos_concept4 <- data_emos_pos_concept4[, -c(1)]

# join all dfs
data_emos_pos <- merge(data_emos_pos_concept1, data_emos_pos_concept2, all.x = TRUE)
data_emos_pos <- merge(data_emos_pos, data_emos_pos_concept3, all.x = TRUE)
data_emos_pos <- merge(data_emos_pos, data_emos_pos_concept4, all.x = TRUE)

# prep for single radar graphs
# check out data for reference
data_emos_pos

# set radar graph max, min, interval and individual values
max <- 120
min <- 0
interval <- 30 # divide max into 4 intervals

# create variables
# concept 1
concept1_appreciated <- c(max, min, as.numeric(data_emos_pos[1, 2])) 
concept1_confident <- c(max, min, as.numeric(data_emos_pos[2, 2]))
concept1_excited <- c(max, min, as.numeric(data_emos_pos[3, 2]))
concept1_happy <- c(max, min, as.numeric(data_emos_pos[4, 2]))
concept1_relieved <- c(max, min, as.numeric(data_emos_pos[5, 2]))
concept1_satisfied <- c(max, min, as.numeric(data_emos_pos[6, 2]))
# concept 2
concept2_appreciated <- c(max, min, as.numeric(data_emos_pos[1, 3])) 
concept2_confident <- c(max, min, as.numeric(data_emos_pos[2, 3]))
concept2_excited <- c(max, min, as.numeric(data_emos_pos[3, 3]))
concept2_happy <- c(max, min, as.numeric(data_emos_pos[4, 3]))
concept2_relieved <- c(max, min, as.numeric(data_emos_pos[5, 3]))
concept2_satisfied <- c(max, min, as.numeric(data_emos_pos[6, 3]))
# concept 3
concept3_appreciated <- c(max, min, as.numeric(data_emos_pos[1, 4])) 
concept3_confident <- c(max, min, as.numeric(data_emos_pos[2, 4]))
concept3_excited <- c(max, min, as.numeric(data_emos_pos[3, 4]))
concept3_happy <- c(max, min, as.numeric(data_emos_pos[4, 4]))
concept3_relieved <- c(max, min, as.numeric(data_emos_pos[5, 4]))
concept3_satisfied <- c(max, min, as.numeric(data_emos_pos[6, 4]))
# concept 4
concept4_appreciated <- c(max, min, as.numeric(data_emos_pos[1, 5])) 
concept4_confident <- c(max, min, as.numeric(data_emos_pos[2, 5]))
concept4_excited <- c(max, min, as.numeric(data_emos_pos[3, 5]))
concept4_happy <- c(max, min, as.numeric(data_emos_pos[4, 5]))
concept4_relieved <- c(max, min, as.numeric(data_emos_pos[5, 5]))
concept4_satisfied <- c(max, min, as.numeric(data_emos_pos[6, 5]))

# create matrix using list() and cbind(), and turn into df
# concept 1
concept1_radar_pos <- list(concept1_appreciated,
                      concept1_confident,
                      concept1_excited,
                      concept1_happy, 
                      concept1_relieved,
                      concept1_satisfied)
concept1_radar_pos <- as.data.frame(cbind(
                      concept1_appreciated,
                      concept1_confident,
                      concept1_excited,
                      concept1_happy, 
                      concept1_relieved,
                      concept1_satisfied))
concept1_radar_pos
# concept 2
concept2_radar_pos <- list(concept2_appreciated,
                      concept2_confident,
                      concept2_excited,
                      concept2_happy, 
                      concept2_relieved,
                      concept2_satisfied)
concept2_radar_pos <- as.data.frame(cbind(
                      concept2_appreciated,
                      concept2_confident,
                      concept2_excited,
                      concept2_happy, 
                      concept2_relieved,
                      concept2_satisfied))
concept2_radar_pos
# concept 3
concept3_radar_pos <- list(concept3_appreciated,
                      concept3_confident,
                      concept3_excited,
                      concept3_happy, 
                      concept3_relieved,
                      concept3_satisfied)
concept3_radar_pos <- as.data.frame(cbind(
                      concept3_appreciated,
                      concept3_confident,
                      concept3_excited,
                      concept3_happy, 
                      concept3_relieved,
                      concept3_satisfied))
concept3_radar_pos
# concept 4
concept4_radar_pos <- list(concept4_appreciated,
                      concept4_confident,
                      concept4_excited,
                      concept4_happy, 
                      concept4_relieved,
                      concept4_satisfied)
concept4_radar_pos <- as.data.frame(cbind(
                      concept4_appreciated,
                      concept4_confident,
                      concept4_excited,
                      concept4_happy, 
                      concept4_relieved,
                      concept4_satisfied))
concept4_radar_pos

# plot single ratings radar graphs
# update column names
emotions <- c("appreciated",
              "confident",
              "excited",
              "happy",
              "relieved",
              "satisfied")
colnames(concept1_radar_pos) <- c(emotions)
colnames(concept2_radar_pos) <- c(emotions)
colnames(concept3_radar_pos) <- c(emotions)
colnames(concept4_radar_pos) <- c(emotions)

# plot charts
# concept 1
radarchart(concept1_radar_pos,
           #custom polygon
           axistype = 1, # centre axis label only
           pcol = rgb(0.2, 0.5, 0.5, 0.9), # vector of colour codes for plot data
           pfcol = rgb(0.2, 0.5, 0.5, 0.5), # vector of color codes for filling polygons
           plwd = 2, # vector of line widths for plot data
           #custom the grid
           cglcol = "grey", # Line color for radar grids
           cglty = 1, # Line type for radar grids
           axislabcol = "grey", # Line type for radar grids
           caxislabels = seq(min, max, interval), # Character vector for center axis labels
           cglwd = 0.8, # Line width for radar grids
           #custom labels
           #vlcex = 0.8, # Font size magnification for vlabels
           #title = "What positive emotions are associated with Quizlet?"
)
# concept 2
radarchart(concept2_radar_pos,
           #custom polygon
           axistype = 1, 
           pcol = rgb(0.2, 0.5, 0.8, 0.9), 
           pfcol = rgb(0.2, 0.5, 0.8, 0.5), 
           plwd = 2, 
           #custom the grid
           cglcol = "grey", 
           cglty = 1, 
           axislabcol = "grey", 
           caxislabels = seq(min, max, interval), 
           cglwd = 0.8, 
           #custom labels
           #vlcex = 0.8,
           #title = "What positive emotions are associated with Duolingo?"
)          
# concept 3
radarchart(concept3_radar_pos,
           #custom polygon
           axistype = 1, 
           pcol = rgb(0.7, 0.5, 0.1, 0.9), 
           pfcol = rgb(0.7, 0.5, 0.1, 0.5), 
           plwd = 2, 
           #custom the grid
           cglcol = "grey", 
           cglty = 1, 
           axislabcol = "grey", 
           caxislabels = seq(min, max, interval), 
           cglwd = 0.8, 
           #custom labels
           #vlcex = 0.8,
           #title = "What positive emotions are associated with Forest?"
)
# concept 4
radarchart(concept4_radar_pos, 
           #custom polygon
           axistype = 1, 
           pcol = rgb(0.5, 0.2, 0.5, 0.9), 
           pfcol = rgb(0.5, 0.2, 0.5, 0.5), 
           plwd = 2, 
           #custom the grid
           cglcol = "grey", 
           cglty = 1, 
           axislabcol = "grey", 
           caxislabels = seq(min, max, interval), 
           cglwd = 0.8, 
           #custom labels
           #vlcex = 0.8,
           #title = "What positive emotions are associated with StudySmarter?"
)
# create variables for multiple ratings radar graphs
# create variables
# appreciated
appreciated <- c(
  max, 
  min, 
  as.numeric(data_emos_pos[1, 2]), 
  as.numeric(data_emos_pos[1, 3]), 
  as.numeric(data_emos_pos[1, 4]), 
  as.numeric(data_emos_pos[1, 5]))
# confident
confident <- c(
  max, 
  min, 
  as.numeric(data_emos_pos[2, 2]), 
  as.numeric(data_emos_pos[2, 3]), 
  as.numeric(data_emos_pos[2, 4]), 
  as.numeric(data_emos_pos[2, 5]))
# excited
excited <- c(
  max, 
  min, 
  as.numeric(data_emos_pos[3, 2]), 
  as.numeric(data_emos_pos[3, 3]), 
  as.numeric(data_emos_pos[3, 4]), 
  as.numeric(data_emos_pos[3, 5]))
# happy
happy <- c(
  max, 
  min, 
  as.numeric(data_emos_pos[4, 2]), 
  as.numeric(data_emos_pos[4, 3]), 
  as.numeric(data_emos_pos[4, 4]), 
  as.numeric(data_emos_pos[4, 5]))
# relieved
relieved <- c(
  max, 
  min, 
  as.numeric(data_emos_pos[5, 2]), 
  as.numeric(data_emos_pos[5, 3]), 
  as.numeric(data_emos_pos[5, 4]), 
  as.numeric(data_emos_pos[5, 5]))
# satisfied
satisfied <- c(
  max, 
  min, 
  as.numeric(data_emos_pos[6, 2]), 
  as.numeric(data_emos_pos[6, 3]), 
  as.numeric(data_emos_pos[6, 4]), 
  as.numeric(data_emos_pos[6, 5]))

# create matrix using list() and cbind(), and turn into df
allRadar_pos <- list(
  appreciated, 
  confident, 
  excited, 
  happy, 
  relieved, 
  satisfied) 
allRadar_pos <- as.data.frame(cbind(
  appreciated, 
  confident, 
  excited, 
  happy, 
  relieved, 
  satisfied))
allRadar_pos

# pimp out radar chart
colors_border = c(rgb(0.2, 0.5, 0.5, 0.9), 
                  rgb(0.2, 0.5, 0.8, 0.9), 
                  rgb(0.7, 0.5, 0.1, 0.9), 
                  rgb(0.5, 0.2, 0.5, 0.9)) # vector coded as var

colors_in = c(rgb(0.2, 0.5, 0.5, 0.4), 
              rgb(0.2, 0.5, 0.8, 0.4), 
              rgb(0.7, 0.5, 0.1, 0.4), 
              rgb(0.5, 0.2, 0.5, 0.4)) # vector coded as var

radarchart(allRadar_pos,  
           #custom polygon
           axistype = 1, # centre axis label only
           pcol = colors_border, # var of colour codes for plot data
           pfcol = colors_in, # var of color codes for filling polygons
           plwd = 2, # vector of line widths for plot data
           plty = 1, # vector of line types for plot data (repeatedly used)
           #custom the grid
           cglcol = "grey", # Line color for radar grids
           cglty = 1, # Line type for radar grids
           axislabcol = "grey", # Line type for radar grids
           caxislabels = seq(min, max, interval), # Character vector for center axis labels
           cglwd = 0.8, # Line width for radar grids
           #custom labels
           #vlcex = 0.8, # Font size magnification for vlabels
           #title = "What positive emotions are associated with the 5 most popular EdTech brands?"
)
```

What kind of descriptive words or emotions are associated with each concept?
- negative
```{r}
# concept1
# select columns
data_emos_neg_concept1 <- data_concept1 %>%
  dplyr::select(ID,
                angry,
                stressful,
                disappointed,
                frustrated,
                anxious,
                confused) %>%
  # filter last row (already counted totals)
  filter(ID == 195) %>%
  # gather columns into rows
  gather("neg_emotions", "concept1_count", 2:7)

# change "count" column to numeric
data_emos_neg_concept1$concept1_count <- as.numeric(data_emos_neg_concept1$concept1_count)

# remove ID column
data_emos_neg_concept1 <- data_emos_neg_concept1[, -c(1)]


# concept 2
# select columns
data_emos_neg_concept2 <- data_concept2 %>%
  dplyr::select(ID,
                angry,
                stressful,
                disappointed,
                frustrated,
                anxious,
                confused) %>%
  # filter last row (already counted totals)
  filter(ID == 195) %>%
  # gather columns into rows
  gather("neg_emotions", "concept2_count", 2:7)

# change "count" column to numeric
data_emos_neg_concept2$concept2_count <- as.numeric(data_emos_neg_concept2$concept2_count)

# remove ID column
data_emos_neg_concept2 <- data_emos_neg_concept2[, -c(1)]


# concept 3
# select columns
data_emos_neg_concept3 <- data_concept3 %>%
  dplyr::select(ID,
                angry,
                stressful,
                disappointed,
                frustrated,
                anxious,
                confused) %>%
  # filter last row (already counted totals)
  filter(ID == 186) %>%
  # gather columns into rows
  gather("neg_emotions", "concept3_count", 2:7)

# change "count" column to numeric
data_emos_neg_concept3$concept3_count <- as.numeric(data_emos_neg_concept3$concept3_count)

# remove ID column
data_emos_neg_concept3 <- data_emos_neg_concept3[, -c(1)]


# concept 4
# select columns
data_emos_neg_concept4 <- data_concept4 %>%
  dplyr::select(ID,
                angry,
                stressful,
                disappointed,
                frustrated,
                anxious,
                confused) %>%
  # filter last row (already counted totals)
  filter(ID == 186) %>%
  # gather columns into rows
  gather("neg_emotions", "concept4_count", 2:7)

# change "count" column to numeric
data_emos_neg_concept4$concept4_count <- as.numeric(data_emos_neg_concept4$concept4_count)

# remove ID column
data_emos_neg_concept4 <- data_emos_neg_concept4[, -c(1)]


# join all dfs
data_emos_neg <- merge(data_emos_neg_concept1, data_emos_neg_concept2, all.x = TRUE)
data_emos_neg <- merge(data_emos_neg, data_emos_neg_concept3, all.x = TRUE)
data_emos_neg <- merge(data_emos_neg, data_emos_neg_concept4, all.x = TRUE)

# radar graphs
# check out data for reference
data_emos_neg

# set radar graph max, min, interval and individual values
max <- 60
min <- 0
interval <- 15 # divide max into 4 intervals

# create variables
# concept 1
concept1_angry <- c(max, min, as.numeric(data_emos_neg[1, 2])) 
concept1_anxious <- c(max, min, as.numeric(data_emos_neg[2, 2]))
concept1_confused <- c(max, min, as.numeric(data_emos_neg[3, 2]))
concept1_disappointed <- c(max, min, as.numeric(data_emos_neg[4, 2]))
concept1_frustrated <- c(max, min, as.numeric(data_emos_neg[5, 2]))
concept1_stressful <- c(max, min, as.numeric(data_emos_neg[6, 2]))
# concept 2
concept2_angry <- c(max, min, as.numeric(data_emos_neg[1, 3])) 
concept2_anxious <- c(max, min, as.numeric(data_emos_neg[2, 3]))
concept2_confused <- c(max, min, as.numeric(data_emos_neg[3, 3]))
concept2_disappointed <- c(max, min, as.numeric(data_emos_neg[4, 3]))
concept2_frustrated <- c(max, min, as.numeric(data_emos_neg[5, 3]))
concept2_stressful <- c(max, min, as.numeric(data_emos_neg[6, 3]))
# concept 3
concept3_angry <- c(max, min, as.numeric(data_emos_neg[1, 4])) 
concept3_anxious <- c(max, min, as.numeric(data_emos_neg[2, 4]))
concept3_confused <- c(max, min, as.numeric(data_emos_neg[3, 4]))
concept3_disappointed <- c(max, min, as.numeric(data_emos_neg[4, 4]))
concept3_frustrated <- c(max, min, as.numeric(data_emos_neg[5, 4]))
concept3_stressful <- c(max, min, as.numeric(data_emos_neg[6, 4]))
# concept 4
concept4_angry <- c(max, min, as.numeric(data_emos_neg[1, 5])) 
concept4_anxious <- c(max, min, as.numeric(data_emos_neg[2, 5]))
concept4_confused <- c(max, min, as.numeric(data_emos_neg[3, 5]))
concept4_disappointed <- c(max, min, as.numeric(data_emos_neg[4, 5]))
concept4_frustrated <- c(max, min, as.numeric(data_emos_neg[5, 5]))
concept4_stressful <- c(max, min, as.numeric(data_emos_neg[6, 5]))

# create matrix using list() and cbind(), and turn into df
# concept 1
concept1_radar_neg <- list(concept1_angry,
                      concept1_anxious,
                      concept1_confused,
                      concept1_disappointed, 
                      concept1_frustrated,
                      concept1_stressful)
concept1_radar_neg <- as.data.frame(cbind(
                      concept1_angry,
                      concept1_anxious,
                      concept1_confused,
                      concept1_disappointed, 
                      concept1_frustrated,
                      concept1_stressful))
concept1_radar_neg
# concept 2
concept2_radar_neg <- list(concept2_angry,
                      concept2_anxious,
                      concept2_confused,
                      concept2_disappointed, 
                      concept2_frustrated,
                      concept2_stressful)
concept2_radar_neg <- as.data.frame(cbind(
                      concept2_angry,
                      concept2_anxious,
                      concept2_confused,
                      concept2_disappointed, 
                      concept2_frustrated,
                      concept2_stressful))
concept2_radar_neg
# concept 3
concept3_radar_neg <- list(concept3_angry,
                      concept3_anxious,
                      concept3_confused,
                      concept3_disappointed, 
                      concept3_frustrated,
                      concept3_stressful)
concept3_radar_neg <- as.data.frame(cbind(
                      concept3_angry,
                      concept3_anxious,
                      concept3_confused,
                      concept3_disappointed, 
                      concept3_frustrated,
                      concept3_stressful))
concept3_radar_neg
# concept 4
concept4_radar_neg <- list(concept4_angry,
                      concept4_anxious,
                      concept4_confused,
                      concept4_disappointed, 
                      concept4_frustrated,
                      concept4_stressful)
concept4_radar_neg <- as.data.frame(cbind(
                      concept4_angry,
                      concept4_anxious,
                      concept4_confused,
                      concept4_disappointed, 
                      concept4_frustrated,
                      concept4_stressful))
concept4_radar_neg

# plot single ratings radar graphs
# update column names
emotions <- c("angry",
              "anxious",
              "confused",
              "disappointed",
              "frustrated",
              "stressful")
colnames(concept1_radar_neg) <- c(emotions)
colnames(concept2_radar_neg) <- c(emotions)
colnames(concept3_radar_neg) <- c(emotions)
colnames(concept4_radar_neg) <- c(emotions)

# plot charts
# concept 1
radarchart(concept1_radar_neg,
           #custom polygon
           axistype = 1, # centre axis label only
           pcol = rgb(0.2, 0.5, 0.5, 0.9), # vector of colour codes for plot data
           pfcol = rgb(0.2, 0.5, 0.5, 0.5), # vector of color codes for filling polygons
           plwd = 2, # vector of line widths for plot data
           #custom the grid
           cglcol = "grey", # Line color for radar grids
           cglty = 1, # Line type for radar grids
           axislabcol = "grey", # Line type for radar grids
           caxislabels = seq(min, max, interval), # Character vector for center axis labels
           cglwd = 0.8, # Line width for radar grids
           #custom labels
           #vlcex = 0.8, # Font size magnification for vlabels
           #title = "What negative emotions are associated with Quizlet?"
)
# concept 2
radarchart(concept2_radar_neg,
           #custom polygon
           axistype = 1, 
           pcol = rgb(0.2, 0.5, 0.8, 0.9), 
           pfcol = rgb(0.2, 0.5, 0.8, 0.5), 
           plwd = 2, 
           #custom the grid
           cglcol = "grey", 
           cglty = 1, 
           axislabcol = "grey", 
           caxislabels = seq(min, max, interval), 
           cglwd = 0.8, 
           #custom labels
           #vlcex = 0.8,
           #title = "What negative emotions are associated with Duolingo?"
)          
# concept 3
radarchart(concept3_radar_neg,
           #custom polygon
           axistype = 1, 
           pcol = rgb(0.7, 0.5, 0.1, 0.9), 
           pfcol = rgb(0.7, 0.5, 0.1, 0.5), 
           plwd = 2, 
           #custom the grid
           cglcol = "grey", 
           cglty = 1, 
           axislabcol = "grey", 
           caxislabels = seq(min, max, interval), 
           cglwd = 0.8, 
           #custom labels
           #vlcex = 0.8,
           #title = "What negative emotions are associated with Forest?"
)
# concept 4
radarchart(concept4_radar_neg, 
           #custom polygon
           axistype = 1, 
           pcol = rgb(0.5, 0.2, 0.5, 0.9), 
           pfcol = rgb(0.5, 0.2, 0.5, 0.5), 
           plwd = 2, 
           #custom the grid
           cglcol = "grey", 
           cglty = 1, 
           axislabcol = "grey", 
           caxislabels = seq(min, max, interval), 
           cglwd = 0.8, 
           #custom labels
           #vlcex = 0.8,
           #title = "What negative emotions are associated with StudySmarter?"
)


# create variables for multiple ratings radar graphs
# create variables
# angry
angry <- c(
  max, 
  min, 
  as.numeric(data_emos_neg[1, 2]), 
  as.numeric(data_emos_neg[1, 3]), 
  as.numeric(data_emos_neg[1, 4]), 
  as.numeric(data_emos_neg[1, 5]))
# anxious
anxious <- c(
  max, 
  min, 
  as.numeric(data_emos_neg[2, 2]), 
  as.numeric(data_emos_neg[2, 3]), 
  as.numeric(data_emos_neg[2, 4]), 
  as.numeric(data_emos_neg[2, 5]))
# confused
confused <- c(
  max, 
  min, 
  as.numeric(data_emos_neg[3, 2]), 
  as.numeric(data_emos_neg[3, 3]), 
  as.numeric(data_emos_neg[3, 4]), 
  as.numeric(data_emos_neg[3, 5]))
# disappointed
disappointed <- c(
  max, 
  min, 
  as.numeric(data_emos_neg[4, 2]), 
  as.numeric(data_emos_neg[4, 3]), 
  as.numeric(data_emos_neg[4, 4]), 
  as.numeric(data_emos_neg[4, 5]))
# frustrated
frustrated <- c(
  max, 
  min, 
  as.numeric(data_emos_neg[5, 2]), 
  as.numeric(data_emos_neg[5, 3]), 
  as.numeric(data_emos_neg[5, 4]), 
  as.numeric(data_emos_neg[5, 5]))
# stressful
stressful <- c(
  max, 
  min, 
  as.numeric(data_emos_neg[6, 2]), 
  as.numeric(data_emos_neg[6, 3]), 
  as.numeric(data_emos_neg[6, 4]), 
  as.numeric(data_emos_neg[6, 5]))

# create matrix using list() and cbind(), and turn into df
allRadar_neg <- list(
  angry, 
  anxious, 
  confused, 
  disappointed, 
  frustrated, 
  stressful) 
allRadar_neg <- as.data.frame(cbind(
  angry, 
  anxious, 
  confused, 
  disappointed, 
  frustrated, 
  stressful))
allRadar_neg

# pimp out radar chart
colors_border = c(rgb(0.2, 0.5, 0.5, 0.9), 
                  rgb(0.2, 0.5, 0.8, 0.9), 
                  rgb(0.7, 0.5, 0.1, 0.9), 
                  rgb(0.5, 0.2, 0.5, 0.9)) # vector coded as var

colors_in = c(rgb(0.2, 0.5, 0.5, 0.4), 
              rgb(0.2, 0.5, 0.8, 0.4), 
              rgb(0.7, 0.5, 0.1, 0.4), 
              rgb(0.5, 0.2, 0.5, 0.4)) # vector coded as var

radarchart(allRadar_neg,  
           #custom polygon
           axistype = 1, # centre axis label only
           pcol = colors_border, # var of colour codes for plot data
           pfcol = colors_in, # var of color codes for filling polygons
           plwd = 2, # vector of line widths for plot data
           plty = 1, # vector of line types for plot data (repeatedly used)
           #custom the grid
           cglcol = "grey", # Line color for radar grids
           cglty = 1, # Line type for radar grids
           axislabcol = "grey", # Line type for radar grids
           caxislabels = seq(min, max, interval), # Character vector for center axis labels
           cglwd = 0.8, # Line width for radar grids
           #custom labels
           #vlcex = 0.8, # Font size magnification for vlabels
           #title = "What negative emotions are associated with the 5 most popular EdTech brands?"
)
```

-----------
Text mining
-----------

Select appropriate columns for text mining
------------------------------------------

```{r}
# Select columns
data_concept1_text <- data_concept1 %>%
  select(
    "conceptNum",
    "describeConcept")

data_concept2_text <- data_concept2 %>%
  select(
    "conceptNum",
    "describeConcept")

data_concept3_text <- data_concept3 %>%
  select(
    "conceptNum",
    "describeConcept")

data_concept4_text <- data_concept4 %>%
  select(
    "conceptNum",
    "describeConcept")

# rename columns
names(data_concept1_text) <- c("rating", "text")
names(data_concept2_text) <- c("rating", "text")
names(data_concept3_text) <- c("rating", "text")
names(data_concept4_text) <- c("rating", "text")

# remove blank (NA) rows
data_concept1_text <- dplyr::filter(data_concept1_text, !is.na(text))
data_concept2_text <- dplyr::filter(data_concept2_text, !is.na(text))
data_concept3_text <- dplyr::filter(data_concept3_text, !is.na(text))
data_concept4_text <- dplyr::filter(data_concept4_text, !is.na(text))
```


# Define 'stopwords'
--------------------

# List of stopword languages: https://www.rdocumentation.org/packages/stopwords/versions/1.0

```{r}
my_stopwords <- stopwords("en")
#my_stopwords <- stopwords("german")
#my_stopwords <- stopwords("french")

```


# Clean text
# ----------

# To analyse data one concept at a time

```{r}
# swap out each concept to analyse one at a time
data <- data_concept1_text
#data <- data_concept2_text
#data <- data_concept3_text
#data <- data_concept4_text

```

# This part splits comments up by the full stops, so each sentence is treated as a separate comment. 
# It also removes the stopwords, replaces abbreviations, replaces symbols, removes unnecessary punctuation and replaces numbers for easier and better text mining.

```{r}
# split up sentences via full-stops
splitPunc <- strsplit(data$text, split = "\\.")
data <- data.frame(rating = rep(data$rating, sapply(splitPunc, length)), text = unlist(splitPunc))

# convert columns back to characters
data[] <- lapply(data, as.character)

# make data lowercase
x <- data$text

lower_x <- x %>%
  tolower() # lowercase function
  
data$text <- lower_x

# clean up text in new df called "data_clean"
data_clean <- data

y <- data_clean$text

clean_y <- y %>%
  tolower() %>% # lowercase function
  replace_abbreviation() %>% # replace abbreviations function
  replace_symbol() %>% # replace symbols function
  removePunctuation() %>% # remove punctuation function
  replace_number() %>% # replace numbers with words function
  removeWords(my_stopwords) # remove stopwords function
  
data_clean$text <- clean_y

# count number of words per row
data_clean$numWords <- sapply(data_clean$text, function(x) length(unlist(strsplit(as.character(x), "\\W+"))))

# remove blank rows 
data_clean <- data_clean %>%
  filter(numWords != 0)

# add in ID column
data_clean$ID <- seq.int(nrow(data_clean))

```


# Mine single words
# -----------------

# Count the number of single words in the text column. 

```{r}
count_words <- data_clean %>%
  unnest_tokens(word, text) %>%
  count(word, sort = TRUE) %>%
  ungroup()

# show words freq data set
count_words

```


# Filter one common word. 

```{r}
# filter word
dplyr::filter(data, grepl("happ", text))

```


# Filter two common words. 

```{r}
# filter rows containing both words
dplyr::filter(data, grepl("happ", text) & grepl("calm", text))

# filter rows containing one of these two words
dplyr::filter(data, grepl("happ", text) | grepl("calm", text))

```


# Create graphs of most common words
# ----------------------------------

# To analyse data all concepts together (for graph) create a separate df for each analysed concept 'count_words' 

```{r}
#data_concept1_graph <- count_words
#data_concept2_graph <- count_words
#data_concept3_graph <- count_words
data_concept4_graph <- count_words
```


# create graph

```{r}
# add concept number to each df
data_concept1_graph$conceptNum <- 1 
data_concept2_graph$conceptNum <- 2 
data_concept3_graph$conceptNum <- 3 
data_concept4_graph$conceptNum <- 4 

# bind all concepts together
data_conceptAll_graph <- dplyr::bind_rows(data_concept1_graph, data_concept2_graph)
data_conceptAll_graph <- dplyr::bind_rows(data_conceptAll_graph, data_concept3_graph)
data_conceptAll_graph <- dplyr::bind_rows(data_conceptAll_graph, data_concept4_graph)

# create graph
data_conceptAll_graph %>%
  filter(n >= 10) %>%
  group_by(conceptNum) %>%
  arrange(n) %>%
  ungroup() %>%
  mutate(word = factor(word, unique(word))) %>%
  ggplot(aes(word, n, fill = conceptNum)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ conceptNum, ncol = 2, scales = "free") +
  labs(x = "Word count", y = NULL) +
  coord_flip()

```
